Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-23 tsibbletalk.Rmd
caption for figure 2

```{r tourism-linking-fig, fig.cap = "Coordinated views generated from the \\code{tourism\\_shared} with persistent linked brushing."}
include_graphics("img/tourism-linking.png")
```

>>>>

```{r tourism-linking-fig, fig.cap = "Snapshot of exploring an ensemble of linked plots of the Australian tourism data, built on a \\code{tourism\\_shared} object. It also illustrates persistent linked brushing to compare two groups."}
include_graphics("img/tourism-linking.png")
```

### 2020-09-23 tsibbletalk.tex
caption for figure 2

\caption[Coordinated views generated from the \code{tourism\_shared} with persistent linked brushing]{Coordinated views generated from the \code{tourism\_shared} with persistent linked brushing.}\label{fig:tourism-linking-fig}
\end{figure}
\end{Schunk}

>>>>

\caption[Snapshot of exploring an ensemble of linked plots of the Australian tourism data, built on a \code{tourism\_shared} object]{Snapshot of exploring an ensemble of linked plots of the Australian tourism data, built on a \code{tourism\_shared} object. It also illustrates persistent linked brushing to compare two groups.}\label{fig:tourism-linking-fig}
\end{figure}
\end{Schunk}
